### 2018-03-19 submission/manuscript.Rmd
remove extras in discussion

In this study we show that the number of OTUs, error rate, and chimera prevalence are HiFi DNA polymerase dependent [Figure 1-2 & 4-5]. These differences are important because many diversity metrics rely on this measure as part of their calculations (e.g. richness). Additionally, the earlier detection of differences in total number of OTUs between HiFi DNA polymerases in the mock versus fecal samples might indicate that high biomass samples may underestimate the biases present within low biomass samples. Importantly, many of these differences are due to undetected chimeras that cannot be fully removed using standard bioinformatic approaches. This is important because it suggests that some of the diversity differences between studies can be attributed to differences in HiFi DNA polyermase used.

@@

Our observations suggest that there are clear HiFi DNA polymerase dependent differences in error rate and chimera prevalence that cannot be fully removed using bioinformatic approaches [Figure 4 & 5]. Although this variation may be due to the DNA polymerase family, the highest and lowest chimera rates both belonged to a family A polymerase (Platinum and Accuprime^TM^ respectively) [@polymerase_Ishino_2014]. Additionally, based on the material safety data sheet (MSDS) the differences between the two HiFi DNA polymerases are not immediately apparent. Both HiFi DNA polymerases contain a recombinant *Taq* DNA polymerase, a *Pyrococcus* spp GB-D polymerase and a platinum *Taq* antibody. With everything else being equal, it is possible that differences in how the recombinant *Taq* was generated could be a contributing factor for the differences in chimera rate between the different HiFi DNA polymerases.

>>>>

In this study we show that the number of OTUs, error rate, and chimera prevalence are HiFi DNA polymerase dependent [Figure 1-2 & 4-5]. These differences are important because many diversity metrics rely on this measure as part of their calculations (e.g. richness). Additionally, the earlier detection of differences in total number of OTUs between HiFi DNA polymerases in the mock versus fecal samples might indicate that high biomass samples may underestimate the biases present within low biomass samples. Importantly, many of these differences are due to undetected chimeras that cannot be fully removed using standard bioinformatic approaches. This suggests that some of the diversity differences between studies can be attributed to differences in HiFi DNA polyermase used.

@@

Although the variation in error rate and chimera prevalence may be due to the DNA polymerase family, the highest and lowest chimera rates both belonged to a family A polymerase (Platinum and Accuprime^TM^ respectively) [@polymerase_Ishino_2014]. Additionally, based on the material safety data sheet (MSDS) the differences between the two HiFi DNA polymerases are not immediately apparent. Both HiFi DNA polymerases contain a recombinant *Taq* DNA polymerase, a *Pyrococcus* spp GB-D polymerase and a platinum *Taq* antibody. With everything else being equal, it is possible that differences in how the recombinant *Taq* was generated could be a contributing factor for the differences observed between the HiFi DNA polymerases.

### 2018-03-19 submission/manuscript.tex
remove extras in discussion

In this study we show that the number of OTUs, error rate, and chimera
prevalence are HiFi DNA polymerase dependent {[}Figure 1-2 \& 4-5{]}.
These differences are important because many diversity metrics rely on
this measure as part of their calculations (e.g.~richness).
Additionally, the earlier detection of differences in total number of
OTUs between HiFi DNA polymerases in the mock versus fecal samples might
indicate that high biomass samples may underestimate the biases present
within low biomass samples. Importantly, many of these differences are
due to undetected chimeras that cannot be fully removed using standard
bioinformatic approaches. This is important because it suggests that
some of the diversity differences between studies can be attributed to
differences in HiFi DNA polyermase used.

@@

Our observations suggest that there are clear HiFi DNA polymerase
dependent differences in error rate and chimera prevalence that cannot
be fully removed using bioinformatic approaches {[}Figure 4 \& 5{]}.
Although this variation may be due to the DNA polymerase family, the
highest and lowest chimera rates both belonged to a family A polymerase
(Platinum and Accuprime\textsuperscript{TM} respectively) (Ishino \&
Ishino, 2014). Additionally, based on the material safety data sheet
(MSDS) the differences between the two HiFi DNA polymerases are not
immediately apparent. Both HiFi DNA polymerases contain a recombinant
\emph{Taq} DNA polymerase, a \emph{Pyrococcus} spp GB-D polymerase and a
platinum \emph{Taq} antibody. With everything else being equal, it is
possible that differences in how the recombinant \emph{Taq} was
generated could be a contributing factor for the differences in chimera
rate between the different HiFi DNA polymerases.

>>>>

In this study we show that the number of OTUs, error rate, and chimera
prevalence are HiFi DNA polymerase dependent {[}Figure 1-2 \& 4-5{]}.
These differences are important because many diversity metrics rely on
this measure as part of their calculations (e.g.~richness).
Additionally, the earlier detection of differences in total number of
OTUs between HiFi DNA polymerases in the mock versus fecal samples might
indicate that high biomass samples may underestimate the biases present
within low biomass samples. Importantly, many of these differences are
due to undetected chimeras that cannot be fully removed using standard
bioinformatic approaches. This suggests that some of the diversity
differences between studies can be attributed to differences in HiFi DNA
polyermase used.

@@

Although the variation in error rate and chimera prevalence may be due
to the DNA polymerase family, the highest and lowest chimera rates both
belonged to a family A polymerase (Platinum and
Accuprime\textsuperscript{TM} respectively) (Ishino \& Ishino, 2014).
Additionally, based on the material safety data sheet (MSDS) the
differences between the two HiFi DNA polymerases are not immediately
apparent. Both HiFi DNA polymerases contain a recombinant \emph{Taq} DNA
polymerase, a \emph{Pyrococcus} spp GB-D polymerase and a platinum
\emph{Taq} antibody. With everything else being equal, it is possible
that differences in how the recombinant \emph{Taq} was generated could
be a contributing factor for the differences observed between the HiFi
DNA polymerases.
